\begin{thebibliography}{99}
    \addcontentsline{toc}{chapter}{TÀI LIỆU THAM KHẢO}

    % --- A. Tài liệu Tiếng Việt ---
    \item[] \textbf{A. Tài liệu Tiếng Việt}

    \bibitem{gso2025} 
    Cục Thống kê đơn vị hành chính. (2025). \textit{Danh mục các đơn vị hành chính Việt Nam}. Truy xuất từ \url{https://danhmuchanhchinh.nso.gov.vn/}

    \bibitem{qh2025} 
    Quốc hội. (2025). \textit{Nghị quyết số 202/2025/QH15 về việc sắp xếp đơn vị hành chính cấp tỉnh}. Truy xuất từ \url{https://thuvienphapluat.vn/}

    \bibitem{ubtvqh2023} 
    Ủy ban Thường vụ Quốc hội. (2023). \textit{Nghị quyết số 35/2023/UBTVQH15 về việc sắp xếp đơn vị hành chính cấp huyện, cấp xã giai đoạn 2023 - 2030}. Truy xuất từ \url{https://vanban.chinhphu.vn/}

    % --- B. Tài liệu Tiếng Anh ---
    \item[] \textbf{B. Tài liệu Tiếng Anh}
    \item[] \textit{I. Sách và Bài báo khoa học (Books \& Papers)}

    \bibitem{chow1994} 
    Chow, G., Heaver, T. D., \& Henriksson, L. E. (1994). Logistics performance: definition and measurement. \textit{International Journal of Physical Distribution \& Logistics Management}, 24(1), 17-28.

    \bibitem{devlin2019} 
    Devlin, J., Chang, M. W., Lee, K., \& Toutanova, K. (2019). BERT: Pre-training of deep bidirectional transformers for language understanding. \textit{Proceedings of NAACL-HLT}, 4171-4186.

    \bibitem{evans2003} 
    Evans, E. (2003). \textit{Domain-driven design: tackling complexity in the heart of software}. Addison-Wesley Professional.

    \bibitem{gruber1993} 
    Gruber, T. R. (1993). A translation approach to portable ontology specifications. \textit{Knowledge Acquisition}, 5(2), 199-220.

    \bibitem{hevner2004} 
    Hevner, A. R., March, S. T., Park, J., \& Ram, S. (2004). Design science in information systems research. \textit{MIS Quarterly}, 28(1), 75-105.

    \bibitem{hwang1981} 
    Hwang, C. L., \& Yoon, K. (1981). \textit{Multiple attribute decision making: methods and applications}. Springer-Verlag.

    \bibitem{kimball2013} 
    Kimball, R., \& Ross, M. (2013). \textit{The data warehouse toolkit: the definitive guide to dimensional modeling (3rd ed.)}. Wiley.

    \bibitem{manning2008} 
    Manning, C. D., Raghavan, P., \& Schütze, H. (2008). \textit{Introduction to information retrieval}. Cambridge University Press.

    \bibitem{martin2017} 
    Martin, R. C. (2017). \textit{Clean architecture: a craftsman's guide to software structure and design}. Prentice Hall.

    \bibitem{phobert2021} 
    Nguyen, D. Q., Nguyen, A. T., \& Pham, S. B. (2021). PhoBERT: Pre-trained language models for Vietnamese. \textit{Findings of EMNLP}, 1037-1042.

    \bibitem{power2002} 
    Power, D. J. (2002). \textit{Decision support systems: concepts and resources for managers}. Greenwood Publishing Group.

    \bibitem{saaty1980} 
    Saaty, T. L. (1980). \textit{The analytic hierarchy process}. McGraw-Hill.

    \bibitem{sprague1982} 
    Sprague Jr, R. H., \& Carlson, E. D. (1982). \textit{Building effective decision support systems}. Prentice-Hall.

    \bibitem{turban2005} 
    Turban, E., Aronson, J. E., \& Liang, T. P. (2005). \textit{Decision support systems and intelligent systems}. Pearson Prentice Hall.

    \item[] \textit{II. Tài liệu Kỹ thuật (Technical Documentation)}

    \bibitem{googlemaps} 
    Google Inc. (2025). Google Maps Platform Documentation – Places API. Available \url{https://developers.google.com/maps/documentation/places/web-service} 

    \bibitem{here} 
    HERE Technologies. (2024). \textit{HERE Location Services Documentation}. Available \url{https://developer.here.com/documentation}

    \bibitem{dotnet8} 
    Microsoft Corporation. (2024). \textit{.NET 8 Documentation}. Available \url{https://learn.microsoft.com/en-us/dotnet/core/whats-new/dotnet-8}

    \bibitem{n8n} 
    n8n GmbH. (2024). \textit{n8n Documentation - Workflow Automation}. Available \url{https://docs.n8n.io/}

    \bibitem{osm} 
    OpenStreetMap Foundation. (2024). \textit{OpenStreetMap Wiki}. Available \url{https://wiki.openstreetmap.org/}

    \bibitem{postgres} 
    PostgreSQL Global Development Group. (2024). \textit{PostgreSQL 15 Documentation}. Available \url{https://www.postgresql.org/docs/15/}

    \bibitem{typesense} 
    Typesense. (2024). \textit{Typesense Guide and API Reference}. Available \url{https://typesense.org/docs/}

\end{thebibliography}